`r title`

### 2018-07-17 lib/report.Rmd
reboot cont..
progress

```{r by_year_by_month_plot}
by_year_by_month_plot
```

@@

```{r by_year_by_hour_of_day, fig.height = 10}
by_year_by_hour_of_day_plot
```

>>>>

```{r by_year_by_month_plot, fig.height = 10}
by_year_by_month_plot
```

@@

```{r by_year_by_hour_of_day, fig.height = 10}
display_if_exists("by_year_by_hour_of_day_plot")
```
